---
title: "Validation Report"
output: pdf_document
---
```{r rsetup, include=FALSE}
# import needed packages, these stay imported in future chunks

```
```{python pysetup, include=FALSE}
# import needed packages, these stay imported in future chunks

```
```{r usercheck, include=FALSE}
# get system information

```
This report was run by user **`r currentuser`** on **`r currentdate`** at **`r currenttime`**

# Report Synopsis
This is a validation report for the CDISC Replication Pilot Project.  The directory of the project is laid out as seen below.  These folders are where the different files for this project are held.  In addition, there are checks in place for the files used in the project to check consistency and completeness.

```{python directorychecks}
# set up directory and file paths

# get contents of desired directories

```

# Directory Outline
The metadata files are located in the following folder:  


The program files are located in the following folder: 


The output files are located in the following folder:  

<!-- end breakout one -->

# File Checks
```{python filechecks}
# get metadata file

# iterate through the metadata dataframe to check if programs and outputs exist
   
   
# create lists of programs and outputs in the respective directory but not in the metadata file

# create boolean variables

```
<!-- end breakout two -->

## Program File Check
The programs in the metadata document were checked against the programs folder, results are as follows: 
```{r badprograms}

```  


```{r badprogrammeta}

```

## Output File Check
The output files in the metadata document were checked against the outputs folder, results are as follows:  

```{r badoutputs}

```  

```{r badoutputmeta}

```
<!-- end breakout three -->

# Output Contents Checks
The text of the output files present in both the metadata document and outputs folder were checked for consistency with the source program files provided.
```{python outputsourcecheck}
# iterate through the metadata dataframe to check output file contents
   
# dataframe of all output files both in metadata and directory

# create boolean to trigger text output for output source check

```
## Sources

```{r badsources}

``` 
<!-- end breakout four -->
